Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-10-02 Chapter_0/04_Manuscript/Manuscript.tex
Worked on revision

\subsection{Permeability Surface}
Using the most parsimonious habitat selection model, we predicted a permeability
surface spanning the entire extent of the KAZA-TFCA. That is, we applied
\ref{EQ1} to our spatial covariates and calculated the selection score \(w(x)\)
for each raster cell. Because our representation of water was dynamic we
collapsed all dynamic water maps into a single map using areas that were covered
by water in at least 10\% of the cases. We used the resulting map to also
calculate a layer returning the distance to water. To reduce the influence of
outliers in predicted permeability scores, we followed \cite{Squires.2013} and
curtailed predicted scores between the 1\textsuperscript{st} and
99\textsuperscript{th} percentile of their original values. To compare
permeability across different regions, we normalized the permeability surface to
a range between 0 (most impermeable) and 1 (most permeable), and we determined
median permeability within and outside the KAZA-TFCA, within and outside
formally protected areas, and within each of the five KAZA-TFCA countries.

@@

\subsection{Habitat Selection Model}
Our most parsimonious habitat selection model (\(\Delta AIC > 2\) than any
alternative model; Table S4) retained the covariates \textit{water},
\textit{distance to water}, \textit{trees}, \textit{shrubs/grassland}, and
\textit{human influence}, beside the fixed covariates \textit{cos(ta)},
\textit{sl}, and \textit{log(sl)} (\Cref{PermeabilityResults}a). With respect to
environmental covariates, dispersers avoided moving through water (\(\beta\) =
-0.53, 95\% CI -0.79 to -0.27) but selected for locations in its vicinity,
although the latter effect was not significant (\(\beta\) = -0.33, 95\% CI =
-0.73 to 0.08). Dispersers avoided areas that were densely covered by trees
(\(\beta\) = -0.31, CI = -0.47 to -0.15) and preferred areas covered by
shrubs/grassland (\(\beta\) = 0.25, 95\% CI = 0.07 to 0.42). Finally, dispersers
avoided areas that were influenced by humans (\(\beta\) = -0.45, 95\% CI = -0.82
to -0.08). With the exepction of \textit{distance to water}, random effects
revealed little variability between dispersal coalitions (Appendix A6).

>>>>

\subsection{Permeability Surface}
Using the most parsimonious habitat selection model, we predicted a permeability
surface spanning the entire extent of the KAZA-TFCA. That is, we applied
\ref{EQ1} to our spatial covariates and calculated the selection score \(w(x)\)
for each raster cell. Because our representation of water was dynamic we
collapsed all dynamic water maps into a single map using areas that were covered
by water in at least 10\% of the cases. We used the resulting map to also
calculate a layer returning the distance to water. Given that the delta only
covers 6\% of the study extent, ignoring seasonality should introduce little
bias in predicted permeability. To reduce the influence of outliers in predicted
permeability scores, we followed \cite{Squires.2013} and curtailed predicted
scores between the 1\textsuperscript{st} and 99\textsuperscript{th} percentile
of their original values. To compare permeability across different regions, we
normalized the permeability surface to a range between 0 (most impermeable) and
1 (most permeable), and we determined median permeability within and outside the
KAZA-TFCA, within and outside formally protected areas, and within each of the
five KAZA-TFCA countries.

@@

\subsection{Habitat Selection Model}
Our most parsimonious habitat selection model (\(\Delta AIC > 2\) than any
alternative model; Table S4) retained the covariates \textit{water},
\textit{distance to water}, \textit{trees}, \textit{shrubs/grassland}, and
\textit{human influence}, beside the fixed covariates \textit{cos(ta)},
\textit{sl}, and \textit{log(sl)} (\Cref{PermeabilityResults}a). With respect to
environmental covariates, dispersers avoided moving through water (\(\beta\) =
-0.53, 95\% CI -0.79 to -0.27, SD\textsubscript{RE} = 0.17) but selected for
locations in its vicinity, although the latter effect was not significant
(\(\beta\) = -0.33, 95\% CI = -0.73 to 0.08, SD\textsubscript{RE} = 0.57).
Dispersers avoided areas that were densely covered by trees (\(\beta\) = -0.31,
CI = -0.47 to -0.15, SD\textsubscript{RE} = 0.14) and preferred areas covered by
shrubs/grassland (\(\beta\) = 0.25, 95\% CI = 0.07 to 0.42, SD\textsubscript{RE}
\(<\) 0.01). Finally, dispersers avoided areas that were influenced by humans
(\(\beta\) = -0.45, 95\% CI = -0.82 to -0.08, SD\textsubscript{RE} = 0.22). With
the exepction of \textit{distance to water}, random effects revealed little
variability between dispersal coalitions (Appendix A6).
